\cursedforest\ - A Random Forest Implementation for ``Big'' and ``Wide'' Data \\ Supplementary Information

### 2016-11-09 doc/publications/plos16/plos16.tex
fixed Gini coefficient
add new figures

\marginpar{figure needs bigger text}
\begin{figure}[tbhp] 
 \begin{adjustwidth}{-1.00in}{0in}
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[totalheight=6cm]{./figs/var_oder.png} 
    \caption{Variable importance of top 20 variables.} 
    \label{fig7:a} 
    \vspace{4ex}
  \end{subfigure}%% 
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[totalheight=6cm]{./figs/var_oob.png}
    \caption{OOB classification error} 
    \label{fig7:b} 
    \vspace{4ex}
  \end{subfigure} 
\caption{{\bf Variable importance (Mean Decrease Gini) and OOB (out of bag) classification error estimate for random
    forests with 100 trees trained on the synthetic dataset of 2.5M features and 5K samples.}  {\bf a)} Variable
  importance of top 20 variables normalized to the sum of the linear model coefficients. {\bf Others} represents
  aggregated importance of variables not present in the linear model. The dotted line represents the original linear
  model coefficients.
 {\bf b)} OOB (out of bag) classification error
  estimate as function of \mtry\ fraction.}
  \label{figure:synth}
\end{adjustwidth}
\end{figure}

@@

In Table~\ref{table3}, we display the top 10 features, ranked by their Gini impurity measure in the random forest model.
\marginpar{This is the Gini impurity measure, The Gini index or coefficient is an economic measure of income inequality}

@@

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l|l|l|l|l|l|p{1cm}|}
\hline
\bf{Genome \%}                      & \bf{Method} & \bf{Error  & \bf{Runtime} & \bf{Memory/Node} \\
\hline

>>>>

\marginpar{figure needs bigger text}
% \begin{figure}[tbhp] 
%  \begin{adjustwidth}{-1.00in}{0in}
%   \begin{subfigure}[b]{0.5\linewidth}
%     \centering
%     \includegraphics[totalheight=6cm]{./figs/var_oder.png} 
%     \caption{Variable importance of top 20 variables.} 
%     \label{fig7:a} 
%     \vspace{4ex}
%   \end{subfigure}%% 
%   \begin{subfigure}[b]{0.5\linewidth}
%     \centering
%     \includegraphics[totalheight=6cm]{./figs/var_oob.png}
%     \caption{OOB classification error} 
%     \label{fig7:b} 
%     \vspace{4ex}
%   \end{subfigure} 
% \caption{{\bf Variable importance (Mean Decrease Gini) and OOB (out of bag) classification error estimate for random
%     forests with 100 trees trained on the synthetic dataset of 2.5M features and 5K samples.}  {\bf a)} Variable
%   importance of top 20 variables normalized to the sum of the linear model coefficients. {\bf Others} represents
%   aggregated importance of variables not present in the linear model. The dotted line represents the original linear
%   model coefficients.
%  {\bf b)} OOB (out of bag) classification error
%   estimate as function of \mtry\ fraction.}
%   \label{figure:synth}
% \end{adjustwidth}
% \end{figure}

\begin{figure}[tbhp] 
 \begin{adjustwidth}{-1.00in}{0in}
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[totalheight=8cm]{./figs/variable_importance.png} 
    \caption{The sum of the variable importance of the 5 significant variables.} 
    \label{fig7:a} 
    \vspace{4ex}
  \end{subfigure}%% 
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[totalheight=8cm]{./figs/out-of-bag-prediction-error.png}
    \caption{OOB classification error} 
    \label{fig7:b} 
    \vspace{4ex}
  \end{subfigure} 
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[totalheight=8cm]{./figs/numnber_of_variables_found.png} 
    \caption{The number of the 5 significant variables found in the top 5.} 
    \label{fig7:a} 
    \vspace{4ex}
  \end{subfigure}%% 
  \begin{subfigure}[b]{0.5\linewidth}
    \centering
    \includegraphics[totalheight=8cm]{./figs/rbo.png}
    \caption{The  rank-biased-overlap measure.} 
    \label{fig7:b} 
    \vspace{4ex}
  \end{subfigure} 
  \caption{{\bf Variable importance (Mean Decrease Gini) and OOB (out of bag) classification error estimate for random
      forests with 100 trees trained on the synthetic dataset of 2.5M features and 5K samples.}  Each measure is shown
    as a function of \mtry and ntree. {\bf a)} The sum of the varible importances for the 5 significant variables.  {\bf
      b)} OOB (out of bag) classification error. {\bf c)} the number of signifivant variables found in the top 5. 
     {\bf d)} The rank-biased-overlap \cite[]{Webber.et.al.2010}. }
  \label{figure:synth}
\end{adjustwidth}
\end{figure}

@@

In Table~\ref{table3}, we display the top 10 features, ranked by their Gini impurity measure in the random forest model.

@@

\begin{table}[!ht]
\begin{minipage}{\textwidth}
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Performance comparison between the different machine learning algorithms.}}
\begin{tabular}{|l|l|l|l|l|l|p{1cm}|}
\hline
\bf{Genome \%}                      & \bf{Method} & \bf{Error}  & \bf{Runtime} & \bf{Memory/Node} \\
\hline
